\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-29 manuscript/main.tex
deleted:    manuscript/July29.pdf 	renamed:    manuscript/main.pdf -> manuscript/Platform-Mediated Consolidation and Online Store Expansion.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

In the real estate market, real estate is not a homogeneous good, and the market is characterized by a large number of firms with no significant barriers to entry. Traditional economic theory suggests that such a market, characterized by substantial competition, numerous firms, and low market concentration, is consistent with real-world observations. For example, Lianjia's offline stores account for less than 5\% of the total, yet Lianjia handles about 20\% of the national transactions. In addition, many well-known agencies, such as Woaiwojia and Centaline Property Agency, operate in this market, indicating a monopolistic competitive environment.

However, when looking at local segmented markets, the monopolistic competition model seems less applicable. In local markets, surrounding neighborhoods share similar community characteristics and public resources. Especially in China's real estate market, most properties are apartments, where the inherent differences between properties are minimal, making them relatively homogeneous goods. In addition, local real estate markets have no barriers to entry or exit, closely resembling perfect competition. From a cost perspective, the real estate market has undergone platform mediated reforms, where data resources have zero marginal cost characteristics and operating costs decrease as the user base expands, suggesting characteristics of a natural monopoly. Under these conditions, the operating position of firms differs significantly from that in a monopolistically competitive market. Due to network effects, an increase in the number of branches of a dominant real estate agency attracts more users, which in turn attracts more real estate listings. This positive feedback loop reinforces the dominant position of firms like Lianjia, leading to the formation of oligopolistic firms. These oligopolistic firms can further maintain their dominant market positions. Thus, even in the absence of barriers to entry and despite the presence of many competing firms, their operations can resemble those of a full monopoly.

In local segmented markets, oligopolistic firms are responsible for increasing network strength and have significant market power. In segmented markets where some oligopolistic firms do not have strong network effects, multiple other firms serve the diverse needs of consumers and expand their scale. The environment of free entry, rapid technological progress, and business model innovation leads to an inclusive competitive landscape in the real estate brokerage market. This environment allows oligopolistic firms to either enhance the strength of their network effects or have their dominant positions challenged. As a result, monopolistic structures emerge from and are subsequently disrupted by competition, allowing real estate intermediaries to continuously evolve and drive the industry's rapid growth. The practical implication is that a competitive oligopolistic structure does not inherently impede competitive efficiency. Instead, it can enhance firm efficiency, thereby facilitating better transactions for buyers and sellers and increasing overall market welfare.

@@

In the future, as the network effects intensify, the real estate market may witness a more pronounced consolidation of market power among a few dominant players. This consolidation can lead to increased efficiencies through economies of scale and scope, where firms leverage their vast data resources and technological advancements to optimize operations and enhance consumer experiences. However, this shift also raises important considerations for regulatory bodies to ensure that the market remains competitive and accessible. The dynamic interplay between technological innovation and market structure will be crucial. As firms like Lianjia continue to innovate, incorporating artificial intelligence, big data analytics, and blockchain for secure transactions, the real estate market could become more transparent and efficient. These advancements could lower transaction costs, reduce information asymmetry, and provide consumers with more personalized services. Furthermore, the global reach of network effects implies that real estate markets across different regions might become more interconnected. This interconnectivity can facilitate cross-border investments and diversify property portfolios for investors, contributing to a more resilient global real estate market.

In conclusion, the evolution of the real estate market towards an oligopolistic competition model, driven by network effects and technological advancements, presents both opportunities and challenges. Policymakers and industry stakeholders must navigate this landscape carefully to harness the benefits of increased efficiency and innovation while safeguarding against potential market power abuses and ensuring equitable access for all participants. This balanced approach will be essential for sustaining long-term growth and enhancing overall market welfare in the real estate industry.

>>>>

In the real estate market, real estate is not a homogeneous good, and therefore, the brokerage market is characterized by a large number of firms with no significant barriers to entry. Traditional economic theory suggests that such a market, characterized by substantial competition, numerous firms, and low market concentration, is consistent with real-world observations. For example, Lianjia's offline stores account for less than 5\% of the total, yet Lianjia handles about 20\% of the national transactions. In addition, many well-known agencies, such as Woaiwojia and Centaline Property Agency, operate in this market, indicating a monopolistic competitive environment.

However, when looking at local segmented markets, the monopolistic competition model seems less applicable. In local markets, surrounding neighborhoods share similar community characteristics and public resources. Especially in China's real estate market, most properties are apartments, where the inherent differences between properties are minimal, making them relatively homogeneous goods. In addition, local real estate markets have no barriers to entry or exit, closely resembling perfect competition. From a cost perspective, the real estate market has undergone platform mediated reforms, where data resources have zero marginal cost characteristics and operating costs decrease as the user base expands, suggesting characteristics of a natural monopoly. Under these conditions, the operating position of firms differs significantly from that in a monopolistically competitive market. Due to network effects, an increase in the number of branches of a dominant real estate agency attracts more users, which in turn attracts more real estate listings. This positive feedback loop reinforces the dominant position of firms like Lianjia, leading to the formation of oligopolistic firms. These oligopolistic firms can further maintain their dominant market positions.

In local segmented markets, oligopolistic firms are responsible for increasing network strength and have significant market power. In segmented markets where some oligopolistic firms do not have strong network effects, multiple other firms serve the diverse needs of consumers and expand their scale. The environment of free entry, rapid technological progress, and business model innovation leads to an inclusive competitive landscape in the real estate brokerage market. This environment allows oligopolistic firms to either enhance the strength of their network effects or have their dominant positions challenged. As a result, monopolistic structures emerge from and are subsequently disrupted by competition, allowing real estate intermediaries to continuously evolve and drive the industry's rapid growth. The practical implication is that a competitive oligopolistic structure does not inherently impede competitive efficiency. Instead, as our empirical findings indicate, the enriched entry and transformations within the market lead to an increase in the number of transactions and house tours. This type of market structure can enhance firm efficiency, thereby facilitating more efficient transactions for buyers and sellers and improving overall market welfare, even though it may impede individual seller welfare.

@@

In the future, as the network effects intensify, the real estate brokerage market may witness a more pronounced consolidation of market power among a few dominant players. This consolidation can lead to increased efficiencies through economies of scale and scope, where firms leverage their vast data resources and technological advancements to optimize operations and enhance consumer experiences. However, this shift also raises important considerations for regulatory bodies to ensure that the market remains competitive and accessible. The dynamic interplay between technological innovation and market structure will be crucial. As firms like Lianjia continue to innovate, incorporating artificial intelligence, big data analytics, and blockchain for secure transactions, the real estate market could become more transparent and efficient. These advancements could lower transaction costs, reduce information asymmetry, and provide consumers with more personalized services. Furthermore, the global reach of network effects implies that real estate brokerage markets across different regions might become more interconnected. This interconnectivity can facilitate cross-city or cross-province investments and diversify property portfolios for investors, contributing to a more resilient real estate market.

In conclusion, the evolution of the real estate brokerage market towards an oligopolistic competition model, driven by network effects and technological advancements, presents both opportunities and challenges. From our empirical findings, this type of market structure can not impede the competitive efficiencies but policymakers and industry stakeholders must navigate this landscape carefully to harness the benefits of increased efficiency and innovation while safeguarding against potential market power abuses and ensuring equitable access for all participants. This balanced approach will be essential for sustaining long-term growth and enhancing overall market welfare in the real estate industry.
